A portable, annotation-based, visual stepper for Common Lisp

### 2020-03-16 paper/paper.tex
Fix comment-reading bug in source-tracking reader
Comments were being incorrectly read as NIL, which frequently messed
up the expansion by Agnostic Lizard.  Traced the problem to the reader
and an incorrect handling of multiple values from readtable entries.

* source-tracking-reader.lisp (read-tracking-source): Fix bug.

* paper/paper.tex (subsection{Source-tracking form reader}): Fix bug.

\begin{verbatim}
(defun read-tracking-source
    (&optional (stream *standard-input*)
       (eof-error-p t) eof-value
       recursive-p (observer #'ignore))
  (let* ((ccs (char-counting-stream stream))
         (*readtable*
           (substitution-table
            *readtable*
            (lambda (shadowed-entry)
              (let (;; correct for the fact that
                    ;; one character of the form
                    ;; has already been read.
                    (start (1- (char-count ccs)))
                    (result (funcall shadowed-entry))
                    (end (char-count ccs)))
                (prog1 result
                  (funcall observer result start end)))))))
    (read ccs eof-error-p eof-value recursive-p)))
\end{verbatim}

>>>>

\begin{verbatim}
(defun read-tracking-source
    (&optional (stream *standard-input*)
       (eof-error-p t) eof-value
       recursive-p (observer #'ignore))
  (let* ((ccs (char-counting-stream stream))
         (*readtable*
           (substitution-table
            *readtable*
            (lambda (shadowed-entry)
              (let (;; correct for the fact that
                    ;; one character of the form
                    ;; has already been read.
                    (start (1- (char-count ccs)))
                    (results (multiple-value-list
                               (funcall shadowed-entry)))
                    (end (char-count ccs)))
                (multiple-value-prog1 (apply #'values results)
                  (when results
                    (funcall observer (car results)
                             start end))))))))
    (read ccs eof-error-p eof-value recursive-p)))
\end{verbatim}
